DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Linear-Time Invariant (LTI) systems are used in several applications
to support non-trivial tasks when applied to embedded systems 
(e.g., robot manipulator, power plants and guidance system). 
In addition, controllers synthesis for LTI systems is richly studied 
by different researchers; however, there are many challenges when 
digital-control systems theory is used due to the effects of finite-word 
length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization 
and quantization noise, which are typically introduced by Analogue-to-Digital 
(ADC) and Digital-to-Analogue (DAC) conversion, which can lead to several 
quantization problems, such as truncation or round-off errors~\cite{astrom1997computer}.

Embedded digital control systems perform computations over digital signals 
to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
expressed as difference equations, transfer functions or state-space equations. 
Here, the focus is on transfer-function and state-space representations. 
The following expression presents the general form of a digital control system 
using the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials, respectively.

In state-space format, the digital control system represents the behavior 
of a system via a state evolution equation $\dot{x}(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
\dot{x}(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

\noindent where A, B, C and D are matrices that fully specify a digital system.

Recently, a new methodology to synthesize digital-control systems was proposed, 
named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
which is based on Counter-Example Guided Inductive Synthesis 
(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} able to produce programs 
for highly non-trivial specifications with a very high degree of automation. 
Program synthesis engines use a specification as the starting point, and subsequently 
produce a sequence of candidate programs from a given template. The candidate programs 
are iteratively refined to eventually satisfy the specification. Modern synthesis engines combine 
automated testing, genetic algorithms and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
Currently, Abate {\it et al.}~\cite{abate2017} synthesize stable, software-implemented 
embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, 
and recently, they also support state-space representation~\cite{abatecav2017}.

>>>>

Linear-Time Invariant (LTI) systems are used in several applications
to support non-trivial tasks when applied to embedded systems 
(e.g., robot manipulator, power plants and guidance system). 
In addition, controllers synthesis for LTI systems is richly studied 
by different researchers~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
however, there are many challenges when 
digital-control systems theory is used due to the finite-word 
length (FWL) effects~\cite{Guang2013, Istepanian2001}, time discretization 
and quantization noise, which are typically introduced by Analogue-to-Digital 
(ADC) and Digital-to-Analogue (DAC) conversion, leading to truncation 
or round-off errors~\cite{astrom1997computer}.

Embedded digital control systems perform computations over digital signals 
to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
expressed as difference equations, transfer functions or state-space equations. 
Here, the focus is on transfer-function and state-space representations. 
The following expression presents the general form of a digital control system 
using the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials, respectively.
%
In state-space format, the digital control system represents the behavior 
of a system via a state evolution equation $\dot{x}(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
\dot{x}(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify a digital system.

Recently, a new methodology to synthesize digital-control systems was proposed, 
named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine able to produce controllers for highly non-trivial 
specifications with a very high degree of automation. Program synthesis engines 
as CEGIS use a specification as the starting point, and subsequently 
produce a sequence of candidate programs from a given template. The candidate programs 
are iteratively refined to eventually satisfy the specification. Modern synthesis engines combine 
automated testing, genetic algorithms and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
Currently, Abate {\it et al.}~\cite{abate2017} synthesize stable, software-implemented 
embedded controllers, along with a physical plant model represented by transfer functions 
or state-space equations~\cite{abate2017,abatecav2017} using a CEGIS-based approach.
